*Supplementary Material 2*

### 2022-06-20 ms/manuscript.Rmd
Use read_from_cache()
as work-around to tar_load(), which stopped working with ftol_cache

tar_load(
  c(
    accs_exclude,
    con_fossil_calibration_tips,
    fern_sanger_seqs_raw,
    fossil_ferns_raw,
    plastid_calibration_dates,
    plastome_alignment,
    plastome_alignment_tbl,
    plastome_metadata_raw_all,
    plastome_metadata_renamed,
    plastome_metadata_renamed,
    plastome_seqs_combined_filtered,
    plastome_tree_rooted,
    ppgi_taxonomy,
    pteridocat,
    raw_fasta_all,
    sanger_accessions_selection,
    sanger_alignment,
    sanger_alignment_tbl,
    sanger_con_tree_dated,
    sanger_con_tree_rooted,
    sanger_seqs_combined_filtered,
    sanger_seqs_rogues_removed,
    ts_fossil_calibration_tips
  ),
  store = ftol_cache
)

# Targets from MS workflow
tar_load(
  c(
    accepted_species,
    bb_coverage_by_rank,
    bb_total_coverage,
    coverage_by_rank,
    crown_ages,
    family_stem_ages,
    fern_monophy_summ_tbl,
    fern_nonmono_gen,
    ftol_ts_comp_mod,
    gb_species_by_year,
    other_dates,
    plastome_iqtree_log,
    ref_files,
    sanger_iqtree_log_2000,
    sanger_sampling,
    total_coverage,
    treepl_cv_results
  ),
  store = here::here("_targets")
)
```

>>>>

accs_exclude <- read_from_cache("accs_exclude", ftol_cache)
con_fossil_calibration_tips <- read_from_cache("con_fossil_calibration_tips", ftol_cache) # nolint
fern_sanger_seqs_raw <- read_from_cache("fern_sanger_seqs_raw", ftol_cache)
fossil_ferns_raw <- read_from_cache("fossil_ferns_raw", ftol_cache)
plastome_alignment <- read_from_cache("plastome_alignment", ftol_cache)
plastome_alignment_tbl <- read_from_cache("plastome_alignment_tbl", ftol_cache)
plastome_metadata_raw_all <- read_from_cache("plastome_metadata_raw_all", ftol_cache) # nolint
plastome_metadata_renamed <- read_from_cache("plastome_metadata_renamed", ftol_cache) # nolint
plastome_metadata_renamed <- read_from_cache("plastome_metadata_renamed", ftol_cache) # nolint
plastome_seqs_combined_filtered <- read_from_cache("plastome_seqs_combined_filtered", ftol_cache) # nolint
plastome_tree_rooted <- read_from_cache("plastome_tree_rooted", ftol_cache)
pteridocat <- read_from_cache("pteridocat", ftol_cache)
raw_fasta_all <- read_from_cache("raw_fasta_all", ftol_cache)
sanger_accessions_selection <- read_from_cache("sanger_accessions_selection", ftol_cache) # nolint
sanger_alignment <- read_from_cache("sanger_alignment", ftol_cache)
sanger_alignment_tbl <- read_from_cache("sanger_alignment_tbl", ftol_cache)
sanger_con_tree_rooted <- read_from_cache("sanger_con_tree_rooted", ftol_cache)
sanger_seqs_combined_filtered <- read_from_cache("sanger_seqs_combined_filtered", ftol_cache) # nolint
sanger_seqs_rogues_removed <- read_from_cache("sanger_seqs_rogues_removed", ftol_cache) # nolint
ts_fossil_calibration_tips <- read_from_cache("ts_fossil_calibration_tips", ftol_cache) # nolint

# Targets from MS workflow
tar_load(
  c(
    accepted_species,
    bb_coverage_by_rank,
    bb_total_coverage,
    coverage_by_rank,
    crown_ages,
    family_stem_ages,
    fern_monophy_summ_tbl,
    fern_nonmono_gen,
    ftol_ts_comp_mod,
    gb_species_by_year,
    other_dates,
    plastome_iqtree_log,
    ref_files,
    sanger_iqtree_log_2000,
    sanger_sampling,
    total_coverage,
    treepl_cv_results,
    ppgi_taxonomy,
    sanger_tree_dated
  ),
  store = here::here("_targets")
)
```

### 2022-06-20 ms/si.Rmd
Use read_from_cache()
as work-around to tar_load(), which stopped working with ftol_cache

tar_load(
  c(
    acc_table_long,
    con_fossil_calibration_tips,
    con_fossil_calibrations_for_treepl,
    fossil_ferns_all,
    plastome_seqs_combined_filtered,
    plastome_tree,
    plastome_tree_rooted,
    ppgi_taxonomy,
    sanger_accessions_selection,
    sanger_sampling,
    sanger_con_tree_dated,
    sanger_con_tree_rooted,
    sanger_alignment_tbl,
    ts_fossil_calibration_tips
  ),
  store = ftol_cache
)

# Targets from MS workflow
tar_load(
  c(
    du_dates_all,
    family_stem_ages,
    fern_monophy_summ_tbl,
    fern_nonmono_gen,
    gb_species_by_year,
    other_dates,
    pteridocat_ppgi_diff_notes,
    pteridocat_ppgi_diff_notes_file,
    ref_files,
    spermato_trees,
    ts_family_stem_ages,
    accepted_species,
    ftol_ts_comp_mod
  ),
  store = here::here("_targets")
)
```

>>>>

acc_table_long <- read_from_cache("acc_table_long", ftol_cache)
con_fossil_calibration_tips <- read_from_cache("con_fossil_calibration_tips", ftol_cache) # nolint
con_fossil_calibrations_for_treepl <- read_from_cache("con_fossil_calibrations_for_treepl", ftol_cache) # nolint
fossil_ferns_all <- read_from_cache("fossil_ferns_all", ftol_cache)
plastome_seqs_combined_filtered <- read_from_cache("plastome_seqs_combined_filtered", ftol_cache) # nolint
plastome_tree <- read_from_cache("plastome_tree", ftol_cache)
plastome_tree_rooted <- read_from_cache("plastome_tree_rooted", ftol_cache)
sanger_accessions_selection <- read_from_cache("sanger_accessions_selection", ftol_cache) # nolint
sanger_con_tree_dated <- read_from_cache("sanger_con_tree_dated", ftol_cache)
sanger_con_tree_rooted <- read_from_cache("sanger_con_tree_rooted", ftol_cache)
sanger_alignment_tbl <- read_from_cache("sanger_alignment_tbl", ftol_cache)
ts_fossil_calibration_tips <- read_from_cache("ts_fossil_calibration_tips", ftol_cache) # nolint

# Targets from MS workflow
tar_load(
  c(
    du_dates_all,
    family_stem_ages,
    fern_monophy_summ_tbl,
    fern_nonmono_gen,
    gb_species_by_year,
    other_dates,
    pteridocat_ppgi_diff_notes,
    pteridocat_ppgi_diff_notes_file,
    ref_files,
    spermato_trees,
    ts_family_stem_ages,
    accepted_species,
    ftol_ts_comp_mod,
    ppgi_taxonomy,
    sanger_tree_dated,
    sanger_sampling
  ),
  store = here::here("_targets")
)
```

### 2022-06-20 ms/si2.Rmd
Use read_from_cache()
as work-around to tar_load(), which stopped working with ftol_cache

```{r load-targets-si-2}
# Targets from MS workflow

@@

tar_load(
  c(
    con_fossil_calibration_tips,
    fossil_ferns_raw),
  store = ftol_cache,
)

>>>>

```{r load-targets-si-2}
# Targets from FTOL workflow

@@

con_fossil_calibration_tips <- read_from_cache(
  "con_fossil_calibration_tips", ftol_cache)
fossil_ferns_raw <- read_from_cache(
  "fossil_ferns_raw", ftol_cache
)
